---
title: "Visualizations and Transformations"
tutorial:
  id: "301_q1"
  version: 0.2
  
output:
  learnr::tutorial:
    progressive: false
    allow_skip: true
    css: ["css/nu-theme.css"]
runtime: shiny_prerendered
description: >
  Data Science in R proficiency quiz on visualizations and transformations.
---

```{r setup, include=FALSE}
library(skimr)
library(learnr)
library(tidyverse)
library(tutorialExtras)
library(gradethis)
library(countdown)

gradethis_setup(pass = "submitted",
                fail = "submitted",
                exercise.completion = FALSE,
                error_checker.message = "submitted",
                fail.hint = FALSE
                )

tutorialExtras_setup(is_exam = TRUE,
                     max_retry = 3,
                     retry_cooldown = 24)

knitr::opts_chunk$set(echo = FALSE)

# credit <- ISLR2::Credit |> 
#   janitor::clean_names()
credit <- read_rds("data/credit.rds")

#write_rds(diamonds, "inst/tutorials/quiz-1/data/diamonds.rds")

# auto <- ISLR2::Auto |> 
#   janitor::clean_names() |> 
#   mutate(origin = factor(origin, 
#                          levels = c("1", "2", "3"), 
#                          labels = c("American", "European", "Japanese")))
auto <- read_rds("data/auto.rds")

# bikeshare <- ISLR2::Bikeshare |> 
#   janitor::clean_names()
bikeshare <- read_rds("data/bikeshare.rds")

# diamonds <- diamonds |> 
#   janitor::clean_names()
diamonds <- read_rds("data/diamonds.rds")

sample_data <- ceiling((rand_int*4/10))

rand_q <- c(0, sample(1:3, 1), sample(1:3, 1), sample(1:4, 1), sample(1:3, 1))

data <- c("diamonds", "credit", "auto", "bikeshare")
```

```{r, context = "server"}
lock_server("lock", exclude = c("Name"), num_blanks = FALSE, show_correct = FALSE)
reset_server("reset", file_name = "quiz-1", package_name = "r4dsQuizzes")
```

```{r Name}
# student name
question_text("Name:",
              answer_fn(function(value){
                              if(length(value) >= 1 ) {
                                return(mark_as(TRUE))
                                }
                              return(mark_as(FALSE) )
                              }),
              correct = "submitted",
              incorrect = "submitted",
              allow_retry = FALSE )
```

```{r}
countdown(minutes = 30L, seconds = 0L, top = 0, right = 0, start_immediately = TRUE,
          color_background = "gray80", color_running_background = "#E4E0EE")
```


## Instructions

You have 30 minutes to complete this quiz.

The quiz covers data visualization and transformations.

As always make sure your code is well organized in proper formatting and using tidyverse functions.

Once you are finished:

-   Check Submissions to make sure every question/exercise has been **submitted**.
-   Click the 'Lock Exam' button. You will not be able to make any changes once this is clicked.
-   Once the exam is locked you will be able to click on the 'Download Exam' button.
-   Submit the completed html to Canvas.

## The Data

The following set of questions are based on the ` `r data[sample_data]` ` data set.
A skim, glimpse, and explanation of the variables are provided below.

```{r}
if(sample_data == 1){
  skim(diamonds)
} else if(sample_data == 2){
  skim(credit)
} else if(sample_data == 3){
  skim(auto)
} else{
  skim(bikeshare)
}
```


```{r}
if(sample_data == 1){
  glimpse(diamonds)
} else if(sample_data == 2){
  glimpse(credit)
} else if(sample_data == 3){
  glimpse(auto)
} else{
  glimpse(bikeshare)
}
```


## Question 1

```{r Concept1}
q1 <- list()
q1[[1]] <- question_numeric("How many observations are in the dataset?",
                    answer(53940, correct = TRUE),
                    allow_retry = TRUE,
                    step = 0.01,
                    correct = "submitted",
                    incorrect = "submitted"
                    )
q1[[2]] <- question_numeric("How many observations are in the dataset?",
                    answer(400, correct = TRUE),
                    allow_retry = TRUE,
                    step = 0.01,
                    correct = "submitted",
                    incorrect = "submitted"
                    )
q1[[3]] <- question_numeric("How many observations are in the dataset?",
                    answer(392, correct = TRUE),
                    allow_retry = TRUE,
                    step = 0.01,
                    correct = "submitted",
                    incorrect = "submitted"
                    )
q1[[4]] <- question_numeric("How many observations are in the dataset?",
                    answer(8645, correct = TRUE),
                    allow_retry = TRUE,
                    step = 0.01,
                    correct = "submitted",
                    incorrect = "submitted"
                    )


q1[[sample_data]]
```


```{r Concept2}
q1b <- list()
q1b[[1]] <- question_numeric("How many variables in the dataset are coded as categorical?",
                    answer(3, correct = TRUE),
                    allow_retry = TRUE,
                    step = 0.01,
                    correct = "submitted",
                    incorrect = "submitted"
                    )
q1b[[2]] <- question_numeric("How many variables in the dataset are coded as categorical?",
                    answer(4, correct = TRUE),
                    allow_retry = TRUE,
                    step = 0.01,
                    correct = "submitted",
                    incorrect = "submitted"
                    )
q1b[[3]] <- question_numeric("How many variables in the dataset are coded as categorical?",
                    answer(2, correct = TRUE),
                    allow_retry = TRUE,
                    step = 0.01,
                    correct = "submitted",
                    incorrect = "submitted"
                    )
q1b[[4]] <- question_numeric("How many variables in the dataset are coded as categorical?",
                    answer(3, correct = TRUE),
                    allow_retry = TRUE,
                    step = 0.01,
                    correct = "submitted",
                    incorrect = "submitted"
                    )

q1b[[sample_data]]
```


```{r Concept3}
exam(
  caption = NULL,
  question_wordbank("Which function/verb would you use to...",
                    choices = c("create a new variable", "keep only observations that meet a criteria"),
                    wordbank = c("slice_max()", "count()", "mutate()", "group_by()", "filter()", "select()", "summarize()", "arrange()", "rename()", "relocate()", "slice_min()", "slice_head()"),
                    answer(c("mutate()", "filter()"), correct = TRUE),
                    allow_retry = TRUE,
                    arrange = "ordered",
                    correct = "submitted",
                    incorrect = "submitted",
                    options = list(group = "definition")
                    ),
  question_wordbank("Which function/verb would you use to...",
                    choices = c("orders the rows of a data frame by the values of selected columns", "keep only desired variables"),
                    wordbank = c("slice_max()", "count()", "mutate()", "group_by()", "filter()", "select()", "summarize()", "arrange()", "rename()", "relocate()", "slice_min()", "slice_head()"),
                    answer(c("arrange()", "select()"), correct = TRUE),
                    allow_retry = TRUE,
                    arrange = "ordered",
                    correct = "submitted",
                    incorrect = "submitted",
                    options = list(group = "definition")
                    ),
  question_wordbank("Which function/verb would you use to...",
                    choices = c("compute the mean of a variable", "select only the first n rows of a data frame."),
                    wordbank = c("slice_max()", "count()", "mutate()", "group_by()", "filter()", "select()", "summarize()", "arrange()", "rename()", "relocate()", "slice_min()", "slice_head()"),
                    answer(c("summarize()", "slice_head()"), correct = TRUE),
                    allow_retry = TRUE,
                    arrange = "ordered",
                    correct = "submitted",
                    incorrect = "submitted",
                    options = list(group = "definition")
                    ),
  question_wordbank("Which function/verb would you use to...",
                    choices = c("perform an action per category", "select the rows with the highest n values of a variable."),
                    wordbank = c("slice_max()", "count()", "mutate()", "group_by()", "filter()", "select()", "summarize()", "arrange()", "rename()", "relocate()", "slice_min()", "slice_head()"),
                    answer(c("group_by()", "slice_max()"), correct = TRUE),
                    allow_retry = TRUE,
                    arrange = "ordered",
                    correct = "submitted",
                    incorrect = "submitted",
                    options = list(group = "definition")
                    )
)
```



## Question 2

Recreate the following visualization: 

- If a fixed color is used, you may use any color of your choice.
- If a transparency is used it is equal to 0.25.

```{r, context = "server"}
q2 <- list()

if(sample_data == 1){
  q2[[1]] <- "images/q2_p1_a.png"
  q2[[2]] <- "images/q2_p1_b.png"
  q2[[3]] <- "images/q2_p1_c.png"
} else if(sample_data == 2){
  q2[[1]] <- "images/q2_p2_a.png"
  q2[[2]] <- "images/q2_p2_b.png"
  q2[[3]] <- "images/q2_p2_c.png"
} else if(sample_data == 3){
  q2[[1]] <- "images/q2_p3_a.png"
  q2[[2]] <- "images/q2_p3_b.png"
  q2[[3]] <- "images/q2_p3_c.png"
} else{
  q2[[1]] <- "images/q2_p4_a.png"
  q2[[2]] <- "images/q2_p4_b.png"
  q2[[3]] <- "images/q2_p4_c.png"
}

text_server(id = "Q2", text = htmltools::img(
				src = q2[[rand_q[2]]], width = 300, height = 227
			) )
```


```{r Question2}
text_ui(id = "Q2")
```


```{r Q2, exercise=TRUE}

```

```{r Q2-solution, exercise.reveal_solution = FALSE}
ggplot()
```

```{r Q2-check}
grade_this_code(
  correct = "Submitted",
  incorrect = "Submitted"
)
```

## Question 3

```{r, context = "server"}
q3 <- list()
if(sample_data == 1){
  q3[[1]] <- HTML("Calculate the mean, standard deviation, and count of diamond <code>price</code> for each <code>cut</code>.")
  q3[[2]] <- HTML("Calculate the count of diamonds of each <code>color</code> and arrange from most to least.")
  q3[[3]] <- HTML("Calculate the minimum, maximum, and count of diamond <code>price</code> for each <code>color</code>.")
} else if(sample_data == 2){
  q3[[1]] <- HTML("Calculate the mean, standard deviation, and count of <code>balance</code> for each <code>region</code>.")
  q3[[2]] <- HTML("Calculate the count of observations from each <code>region</code> and arrange from least to greatest.")
  q3[[3]] <- HTML("Calculate the minimum and maximum <code>balance</code> by whether an individual <code>own</code> s a house and if the individual is <code>married</code>. ie: balance of owns a house and married, owns a house and not married, etc.")
} else if(sample_data == 3){
  q3[[1]] <- HTML("Calculate the mean, standard deviation, and count of <code>mpg</code> for each `origin</code>.")
  q3[[2]] <- HTML("Calculate the count of cars of each <code>origin</code> and arrange from most to least.")
  q3[[3]] <- HTML("Calculate the minimum, maximum, and count of <code>mpg</code> for each <code>origin</code>.")
} else{
  q3[[1]] <- HTML("Calculate the mean, standard deviation, and count of <code>bikers</code> for each <code>weathersit</code>.")
  q3[[2]] <- HTML("Calculate the count of <code>weathersit</code> and arrange from most to least.")
  q3[[3]] <- HTML("Calculate the minimum, maximum, and count of <code>bikers</code> for each <code>weathersit</code>.")
}

text_server(id = "Q3", text = q3[[rand_q[3]]])
```


```{r Question3}
text_ui(id = "Q3")
```


```{r Q3, exercise=TRUE}

```

```{r Q3-solution, exercise.reveal_solution = FALSE}
ggplot()
```

```{r Q3-check}
grade_this_code(
  correct = "Submitted",
  incorrect = "Submitted"
)
```

## Question 4

```{r, context = "server"}
#| warning: false
q4 <- list()
if(sample_data == 1){
  q4[[1]] <- HTML("Create a new variable called <code>price_per_carat</code> which is calculated as <code>price</code> divided by <code>carat</code>. Only print the first 3 observations of the data frame and only include the columns used in the calculation in addition to the new variable.")
  q4[[2]] <- HTML("Create a new variable called <code>price_per_carat</code> which is calculated as <code>price</code> divided by <code>carat</code>. Only print the largest 5 observations based on this new variable and only include the columns used in the calculation in addition to the new variable.")
  q4[[3]] <- HTML("Create a new variable called <code>price_per_carat</code> which is calculated as <code>price</code> divided by <code>carat</code>. Move this new variable to the beginning of the data frame and only print the smallest 4 observations based on this new variable.")
  q4[[4]] <- HTML("Create a new variable called <code>price_per_carat</code> which is calculated as <code>price</code> divided by <code>carat</code>. Move this new variable to the beginning of the data frame and only print the last 5 observations of the data frame.")
} else if(sample_data == 2){
  q4[[1]] <- HTML("Create a new variable called <code>prop_limit_used</code> which is calculated as <code>balance</code> divided by <code>limit</code>. Only print the first 3 observations of the data frame and only include the columns used in the calculation in addition to the new variable.")
  q4[[2]] <- HTML("Create a new variable called <code>prop_limit_used</code> which is calculated as <code>balance</code> divided by <code>limit</code>. Only print the largest 5 observations based on this new variable and only include the columns used in the calculation in addition to the new variable.")
  q4[[3]] <- HTML("Create a new variable called <code>prop_limit_used</code> which is calculated as <code>balance</code> divided by <code>limit</code>. Move this new variable to the beginning of the data frame and only print the smallest 4 observations based on this new variable.")
  q4[[4]] <- HTML("Create a new variable called <code>prop_limit_used</code> which is calculated as <code>balance</code> divided by <code>limit</code>. Move this new variable to the beginning of the data frame and only print the last 5 observations of the data frame.")
} else if(sample_data == 3){
  q4[[1]] <- HTML("Create a new variable called <code>power_weight_ratio</code> which is calculated as <code>horsepower</code> divided by <code>weight</code>. Only print the first 3 observations of the data frame and only include the columns used in the calculation in addition to the new variable.")
  q4[[2]] <- HTML("Create a new variable called <code>power_weight_ratio</code> which is calculated as <code>horsepower</code> divided by <code>weight</code>. Only print the largest 5 observations based on this new variable and only include the columns used in the calculation in addition to the new variable.")
  q4[[3]] <- HTML("Create a new variable called <code>power_weight_ratio</code> which is calculated as <code>horsepower</code> divided by <code>weight</code>. Move this new variable to the beginning of the dataframe and only print the smallest 4 observations based on this new variable.")
  q4[[4]] <- HTML("Create a new variable called <code>power_weight_ratio</code> which is calculated as <code>horsepower</code> divided by <code>weight</code>. Move this new variable to the beginning of the dataframe and only print the first 5 observations of the data frame.")
} else{
  q4[[1]] <- HTML("Create a new variable called <code>prop_registered</code> which is calculated as <code>registered</code> divided by <code>bikers</code>. Only print the first 3 observations of the data frame and only include the columns used in the calculation in addition to the new variable.")
  q4[[2]] <- HTML("Create a new variable called <code>prop_registered</code> which is calculated as <code>registered</code> divided by <code>bikers</code>. Only print the largest 5 observations based on this new variable and only include the columns used in the calculation in addition to the new variable.")
  q4[[3]] <- HTML("Create a new variable called <code>prop_registered</code> which is calculated as <code>registered</code> divided by <code>bikers</code>. Move this new variable to the beginning of the data frame and only print the smallest 4 observations based on this new variable.")
  q4[[4]] <- HTML("Create a new variable called <code>prop_registered</code> which is calculated as <code>registered</code> divided by <code>bikers</code>. Move this new variable to the beginning of the data frame and only print the last 5 observations of the data frame.")
}

text_server(id = "Q4", text = q4[[rand_q[4]]])
```


```{r Question4}
text_ui(id = "Q4")
```

```{r Q4, exercise=TRUE}

```

```{r Q4-solution, exercise.reveal_solution = FALSE}
ggplot()
```

```{r Q4-check}
grade_this_code(
  correct = "Submitted",
  incorrect = "Submitted"
)
```

<br>

## Question 5

```{r, context = "server"}
#| warning: false
q5 <- list()
if(sample_data == 1){
  q5[[1]] <- HTML("Plot the relationship of <code>price</code> by <code>carat</code>. Facet by both the variable <code>cut</code> and the variable <code>color</code>.")
  q5[[2]] <- HTML("Plot the relationship of <code>price</code> by <code>carat</code>. Set the shape equal to the variable <code>cut</code> and facet by the variable <code>color</code> with 2 rows.")
  q5[[3]] <- HTML("Plot the relationship of <code>price</code> by <code>carat</code>. Set the color equal to the variable <code>color</code>. Facet by the variable <code>cut</code> and change the scales to free.")
} else if(sample_data == 2){
  q5[[1]] <- HTML("Plot the relationship of <code>limit</code> by <code>income</code>. Facet by both the variable <code>married</code> and the variable <code>cards</code>. use the labeller argument to label both facets.")
  q5[[2]] <- HTML("Plot the relationship of <code>limit</code> by <code>income</code>. Set the shape equal to the variable <code>married</code> and facet by the variable <code>own</code> with 2 rows.")
  q5[[3]] <- HTML("Plot the relationship of <code>limit</code> by <code>income</code>. Set the color equal to the variable <code>own</code>. Facet by the variable <code>married</code> and change the scales to free.")
} else if(sample_data == 3){
  q5[[1]] <- HTML("Plot the relationship of <code>horsepower</code> by <code>weight</code>. Facet by both the variable <code>origin</code> and the variable <code>cylinders</code>.")
  q5[[2]] <- HTML("Plot the relationship of <code>horsepower</code> by <code>weight</code>. Set the shape equal to the variable <code>cylinders</code> and facet by the variable <code>origin</code> with 3 rows.")
  q5[[3]] <- HTML("Plot the relationship of <code>horsepower</code> by <code>weight</code>. Set the color equal to the variable <code>origin</code>. Facet by the variable <code>cylinders</code> and change the scales to free.")
} else{
  q5[[1]] <- HTML("Plot the relationship of <code>bikers</code> by <code>temp</code>. Facet by both the variable <code>weathersit</code> and the variable <code>season</code>.")
  q5[[2]] <- HTML("Plot the relationship of <code>bikers</code> by <code>temp</code>. Set the shape equal to the variable <code>weathersit</code> and facet by the variable <code>month</code> with 4 rows.")
  q5[[3]] <- HTML("Plot the relationship of <code>bikers</code> by <code>temp</code>. Set the color equal to the variable <code>weathersit</code>. Facet by the variable <code>season</code> and change the scales to free.")
}

text_server(id = "Q5", text = q5[[rand_q[5]]])
```


```{r Question5}
text_ui(id = "Q5")
```


```{r Q5, exercise=TRUE}

```

```{r Q5-solution, exercise.reveal_solution = FALSE}
ggplot()
```

```{r Q5-check}
grade_this_code(
  correct = "Submitted",
  incorrect = "Submitted"
)
```

## Submit

Once you are finished:

-   Click **Check Submissions** to make sure all questions and exercises are submitted -- Un-submitted questions will receive a 0.
-   Once all questions/exercises are submitted click the **Lock Exam** button. Once you click this you will not be able to make any changes to your exam!
-   Once the lock is pressed a **Download Exam** option will become available,
-   Download and **Check your HTML!**

-  You have 3 attempts on this proficiency quiz. Submit the quiz you want to be graded to Canvas. The grader will ONLY be grading one quiz per student. You can submit multiple attempts but the grader will only grade your LAST submission.

```{r}
lock_check_ui(id = "lock")
```
<br>
```{r}
lock_button_ui(id = "lock")
```


## Retry

The retry button is available 24 hours after you lock the quiz. 

You have 3 attempts on this quiz. 

Once you click retry, your quiz will be erased and a new set of questions will be generated. Make sure you downloaded your quiz and check that everything is correct **prior to clicking the retry button**. Once you click retry there will be no way to retrieve your prior attempt.


```{r}
reset_button_ui(id = "reset")
```
